\vspace{-2cm} Government websites as data: A methodological pipeline with application to the websites of municipalities in the United States

### 2018-07-13 paper/manuscript.tex
updated the table describing how many republican/democratic cities we have per state
added a note about the size of our corpus (259,099 documents)
moving stuff around and shaping for PA

\end{abstract}
\thispagestyle{empty}
% \doublespacing
% Description of the possible challenges
\section{Introduction}

@@

Information on other covariates (population and median household income - from the American Community Survey 5) was acquired through the API of the U.S. Census Bureau\footnote{\url{https://www.census.gov/data/developers/data-sets.html}}.

@@

This classifier is then used to flag and remove all lines that are not classified as substantively useful. The effect of this process on the corpus is illustrated with the corpus of Anchorage, AK (i.e. a city that isn't part of our sample used in the analysis) as an example in figures \ref{boilerplate_before_after1} to \ref{boilerplate_before_after4} in the appendix. Before the lines identified by the classifier as boilerplate are removed, lines with very few characters and words are the most common. After the removal, the distribution looks more like what it should be - lines of medium length now occur more frequently than extremely short ones (see figures \ref{boilerplate_before_after1} and \ref{boilerplate_before_after2}). Furthermore, lines that are duplicated only a few times rather than dozens, hundreds or even thousands are now more common (see figure \ref{boilerplate_before_after3}). Finally, the position of the line within the documents is not as important to the random forest, and this also shows in the results. However, this feature still has a positive effect, as lines at either end of the document are a bit less common now (see figure \ref{boilerplate_before_after4}).

@@

\input{tables/urlSummary.tex}
%\input{tables/stateUrlSummary.tex}

@@

\newpage
\section*{Appendix}
\begin{figure}[htp]
	\centering
	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
	\label{boilerplate_before_after1}
	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterNwords.pdf}
\end{figure}
\begin{figure}[htp]
	\centering
	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
	\label{boilerplate_before_after2}
	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterFreq.pdf}
\end{figure}
\begin{figure}[htp]
	\centering
	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
	\label{boilerplate_before_after3}
	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterMedianDocMidDist.pdf}
\end{figure}
\begin{figure}[htp]
	\centering
	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
	\label{boilerplate_before_after4}
	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterNchars.pdf}
\end{figure}

>>>>

\end{abstract}
\thispagestyle{empty}
% \doublespacing
% Description of the possible challenges
\doublespacing
\section{Introduction}

@@

Information on other covariates (population and median household income - from the American Community Survey 5) was acquired through the API of the U.S. Census Bureau\footnote{\url{https://www.census.gov/data/developers/data-sets.html}}.
\input{tables/tabCitiesStatesParties.tex}

@@

This classifier is then used to flag and remove all lines that are not classified as substantively useful. The effect of this process on the corpus is illustrated with the corpus of Anchorage, AK (i.e. a city that isn't part of our sample used in the analysis) as an example in Figures \ref{boilerplate_before_after1} to \ref{boilerplate_before_after4}. Before the lines identified by the classifier as boilerplate are removed, lines with very few characters and words are the most common. After the removal, the distribution looks more like what it should be - lines of medium length now occur more frequently than extremely short ones (see figures \ref{boilerplate_before_after1} and \ref{boilerplate_before_after2}). Furthermore, lines that are duplicated only a few times rather than dozens, hundreds or even thousands are now more common (see figure \ref{boilerplate_before_after3}). Finally, the position of the line within the documents is not as important to the random forest, and this also shows in the results. However, this feature still has a positive effect, as lines at either end of the document are a bit less common now (see figure \ref{boilerplate_before_after4}). After all the preprocessing is set and done, our corpus consists of 259,099 documents.

\begin{figure}[htp]
	\centering
	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
	\label{boilerplate_before_after1}
	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterNwords.pdf}
\end{figure}
\begin{figure}[htp]
	\centering
	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
	\label{boilerplate_before_after2}
	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterFreq.pdf}
\end{figure}
\begin{figure}[htp]
	\centering
	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
	\label{boilerplate_before_after3}
	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterMedianDocMidDist.pdf}
\end{figure}
\begin{figure}[htp]
	\centering
	\caption{Effects of the boilerplate classifier on the corpus of the city of Anchorage, AK.}
	\label{boilerplate_before_after4}
	\includegraphics[width=\linewidth]{figures/boilerplateBeforeAfterNchars.pdf}
\end{figure}

@@

%\input{tables/tabCitiesStatesParties.tex}
%\input{tables/stateUrlSummary.tex}

@@

\newpage
\section*{Appendix}
